Age-related changes in plant growth and traits

### 2016-10-25 scripts/RA_figs_20160627.Rmd
new RA plot showing how proportion of energy to different outcomes shift across life

par(mfrow=c(1,1), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
```

#Figure 1 Different species have different RA values. But biggest shift in RA is with age
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
#pdf("figs2/RA/Figure_1_leaf_vs_repro.pdf", height=4.3, width=8)
win.metafile("figs2/RA/Figure_1_leaf_vs_repro.wmf", height=4.3, width=8)
plot
par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

>>>>

par(mfrow=c(1,1), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
```
  data <- data %>% mutate(
    total_inv = repro_inv + growth_leaf + leaf_replacement + growth_stem,
    prop_repro = repro_inv / total_inv,
    prop_leaf_expand = (repro_inv + growth_leaf)/total_inv,
    prop_leaf_replacement = (leaf_replacement+repro_inv + growth_leaf)/ total_inv,
    prop_stem = total_inv/total_inv
  )

View(data)

```{r}
data <- dplyr::select(SummarySppAge[["mean"]],species,age,repro_inv,growth_leaf,leaf_replacement,growth_stem,leaf_shed)

  for(v in c("repro_inv","growth_leaf","leaf_replacement","growth_stem","leaf_shed")) {
    i <- is.na(data[[v]])
    data[[v]][i] <- 0
  }

  for(v in c("growth_leaf")) {
    i <- (data[[v]] < 0)
    data[[v]][i] <- 0
  }

#data <- subset(data,species=="BOLE")
data <- split(data, data$species)

  data[[spp]] <- data[[spp]] %>% mutate(
    total_inv = repro_inv + growth_leaf + leaf_replacement + growth_stem,
    prop_repro = repro_inv / total_inv,
    prop_leaf_expand = (repro_inv + growth_leaf)/total_inv,
    prop_leaf_replacement = (leaf_replacement+repro_inv + growth_leaf)/ total_inv,
    prop_stem = total_inv/total_inv
  )

  plot(prop_repro~age,data[[spp]],pch=16,log="x",ylim=c(0.04,0.96),xlim=c(1.06*1.4,0.94*32),col="white")

  if(spp=="PILI") {
  polygon(x=c(1.4,7,7,1.4),y=c(1,1,0,0),col="burlywood4",density=NA)
  polygon(x=c(1.4,2.4,5,7,7,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
                                           0,0),col="darkseagreen4",density=NA)
  polygon(x=c(1.4,2.4,5,7,7,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
                                         0,0),col="darkseagreen2",density=NA)
  polygon(x=c(1.4,2.4,5,7,7,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
                                         0,0),col="coral3",density=NA)
  text(5,0.1,"reproductive")
  text(1.4,0.18,"additional leaves",adj=0)
  text(3,0.4,"replacement leaves",adj=0)
  text(2,0.7,"additional stems",adj=0)
  }

  if(spp=="PHPH") {
  polygon(x=c(2.4,32,32,2.4),y=c(1,1,0,0),col="burlywood4",density=NA)
  polygon(x=c(2.4,5,7,9,32,32,2.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
                                           data[[spp]]$prop_leaf_replacement[5],0,0),col="darkseagreen4",density=NA)
  polygon(x=c(2.4,5,7,9,32,32,2.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
                                         data[[spp]]$prop_leaf_expand[5],0,0),col="darkseagreen2",density=NA)
  polygon(x=c(2.4,5,7,9,32,32,2.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
                                          data[[spp]]$prop_repro[5],0,0),col="coral3",density=NA)
  text(20,data[[spp]]$prop_repro[5]*.7,"reproductive")
  text(2.5,data[[spp]]$prop_leaf_expand[1]*.3,"additional leaves",adj=0)
  text(5,data[[spp]]$prop_leaf_replacement[4]*.6,"replacement leaves",adj=0)
  text(15,0.9,"additional stems",adj=0)
    }

 if(spp=="BOLE"|spp=="COER"|spp=="HEPU"|spp=="GRSP") {
  polygon(x=c(1.4,9,9,1.4),y=c(1,1,0,0),col="burlywood4",density=NA) 
  polygon(x=c(1.4,2.4,5,7,9,9,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
                                           data[[spp]]$prop_leaf_replacement[5],0,0),col="darkseagreen4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,9,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
                                         data[[spp]]$prop_leaf_expand[5],0,0),col="darkseagreen2",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,9,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
                                          data[[spp]]$prop_repro[5],0,0),col="coral3",density=NA)
  text(8,data[[spp]]$prop_repro[5]*.4,"reproductive",adj=1)
  text(1.5,data[[spp]]$prop_leaf_expand[1]*.5,"additional leaves",adj=0)
  text(4,data[[spp]]$prop_leaf_replacement[3]*.6,"replacement leaves",adj=0)
  text(6,0.9,"additional stems",adj=1)
  }

  if(spp=="BAER"|spp=="EPMI"|spp=="GRBU"|spp=="HATE"|spp=="PELA"|spp=="PUTU"|spp=="LEES"|spp=="PEPU") {
  polygon(x=c(1.4,32,32,1.4),y=c(1,1,0,0),col="burlywood4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
                                           data[[spp]]$prop_leaf_replacement[5],data[[spp]]$prop_leaf_replacement[6],0,0),col="darkseagreen4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
                                         data[[spp]]$prop_leaf_expand[5],data[[spp]]$prop_leaf_expand[6],0,0),col="darkseagreen2",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
                                          data[[spp]]$prop_repro[5],data[[spp]]$prop_repro[6],0,0),col="coral3",density=NA)
  text(20,data[[spp]]$prop_repro[6]*.4,"reproductive")
  text(1.5,data[[spp]]$prop_leaf_expand[1]*.3,"additional leaves",adj=0)
  text(5,data[[spp]]$prop_leaf_replacement[4]*.6,"replacement leaves",adj=0)
  text(15,0.9,"additional stems",adj=0)
  }
  extra.top.left.logx(labels.spp.full(spp),3,1)
}
```

-#Figure 1 Different species have different RA values. But biggest shift in RA is with age
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
#pdf("figs2/RA/Figure_1_leaf_vs_repro.pdf", height=4.3, width=8)
win.metafile("figs2/RA/Figure_1_leaf_vs_repro.wmf", height=4.3, width=8)
plot
par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)
